---
title: "TS% Analysis"
author: "Nick Olech"
date: "2024-10-24"
output: html_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NBA center analysis

I do not believe that Nikola Vucevic played like a top 20 center last season. In a somewhat bad faith analysis, I will look to calculate some advanced analytics from the NBA season last year.

## Import Dataset
```{r}
library(readxl)
setwd(choose.dir())
list.files()


# List all files
csv_files <- list.files(pattern = "\\.csv$")

# Read each file and store in a list
data_list <- lapply(csv_files, read.csv)

# 
names(data_list) <- csv_files

# Make dataset
nba_data <- do.call(rbind, lapply(csv_files, read.csv))
```

## Criteria for Centers
1. Any effective NBA scorer should maintain a relatively high TS%
    - In order to account for volume, I will filter by a ppg benchmark
2. Any effective NBA scorer should maintain a high Asst/TOV ratio
    In order to account for volume, I will filter my minnimun assists
    
    
## Filter all of our data for the center position
```{r}
library(dplyr)
library(tidyr)
library(tidyverse)

centers_filtered <- nba_data %>%
  filter(Pos == "C" | Pos == "C-PF") %>%  
  select(FGA, FT., PTS, G, AST, TOV) 

```

## Use included variables to calculate the true shooting percentage
```{r}

```




