---
title: "TS% Analysis"
author: "Nick Olech"
date: "2024-10-24"
output: html_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NBA center analysis

I do not believe that Nikola Vucevic played like a top 20 center last season. In a somewhat bad faith analysis, I will look to calculate some advanced analytics from the NBA season last year.

## Import Dataset
```{r}
library(readxl)
setwd("C:/Users/nicko/OneDrive/Desktop/Github/Project 2/NbaAgenda/NBADATA")
list.files()

# List all files
csv_files <- list.files(pattern = "\\.csv$")
print(csv_files)

# Read each file and store in a list
data_list <- lapply(csv_files, read.csv)

# 
names(data_list) <- csv_files

# Make dataset
nba_data <- do.call(rbind, lapply(csv_files, read.csv))
```

## Criteria for Centers
1. Any effective NBA scorer should maintain a relatively high TS%
    - In order to account for volume, I will filter by a ppg benchmark
2. An all around  NBA scorer should maintain a high Asst/TOV ratio
    - In order to account for volume, I will filter my minimum assists
3. There are not enough statistics to calculate advanced defensive stats, advanced defensive analytics also 
have some more flaws opposed to offensive ones
   - I.e. lack of on/off ball context 
    
    
## Filter all of our data for the center position

Also add a column for for total points scored and a column for total points from fts.

Can also calculate Assist:TOV Ratio with apg/tov (per game)

True shooting percentage is calculated as follows

TS% = (Total Points Scored)/(2*(FG attempts + .44FT Attempts))

```{r}
library(dplyr)
library(tidyr)
library(tidyverse)

centers_filtered <- nba_data %>%
  filter(Pos == "C" | Pos == "C-PF") %>%  
  select(Player, Pos, MP, FGA, FT., FTA, PTS, G, AST, TOV, PTS) %>%
  mutate(
    total_points = round(PTS*G),
    ft_Points = round(FT.*FTA*G),
    ast_tov_ratio = round(AST/TOV, 2)
  ) %>%
  mutate_all(~ ifelse(is.na(.) | is.nan(.) | is.infinite(.), "", .))  

```

## Now lets make some graph to see the overall landscape of centers in the nba

```{r}

```




